The Ecology of Cloud Computing

### 2022-04-07 paper.tex
Added paragraph about peatland bogs

where $SC$ is the relative Sneakernet carbon (how much carbon emitted by Sneakernet relative to that emitted by internet transfer), $E_{vehicle}$ is the emissions of the vehicle (in g CO2e/km), $d$ the distance of transfer (in km), $E_{internet}$ the emissions of data transmission (in g CO2e/GB) and $s$ the size of the data being transferred (in GB). A 2016 study estimated the energy cost of data transfer as 0.023kWh per gigabyte. \citep{aslan2018electricity} In the United Kingdom, this would emit 5g CO2e/GB. We will take our vehicle as a Mercedes Sprinter (the van used by Royal Mail), which emits approximately 192.6g CO2e/km. \citep{mercedes2019sprinter} We will say our facility is in central London, and our data centre at the Cyxtera Data Centre Campus, a popular data centre campus in Slough - a distance of around 35km. This creates a linear plot from which we can see Sneakernet's carbon emissions break even to the Internet's at a data size of 1348.2GB; that is just one or two regular-sized hard drives! This is even better with electric vehicles; Royal Mail plans to switch to the electric Arrival van, which at most stores 139kWh with a range of 340km \citep{hubbard2021new}. If charged using fossil-fuel generated electricity (the worst-case scenario) this emits 94g CO2e/km, meaning we 'break even' on SneakerNet at 658GB, which one could probably fit on a single laptop. \newline

@@

One could make the analogy that carbon offsetting is the climate equivalent of the payday loan. Sure, your carbon output will balance out (over infinite time), but if you can help it you'd do better to just leave the fossil fuels in the ground in the first place.

>>>>

where $SC$ is the relative Sneakernet carbon (how much carbon emitted by Sneakernet relative to that emitted by internet transfer), $E_{vehicle}$ is the emissions of the vehicle (in g CO2e/km), $d$ the distance of transfer (in km), $E_{internet}$ the emissions of data transmission (in g CO2e/GB) and $s$ the size of the data being transferred (in GB). A 2016 study estimated the energy cost of data transfer as 0.023kWh per gigabyte. \citep{aslan2018electricity} In the United Kingdom, this would emit 5g CO2e/GB. We will take our vehicle as a Mercedes Sprinter (the van used by Royal Mail), which emits approximately 192.6g CO2e/km. \citep{mercedes2019sprinter} We will say our facility is in central London, and our data centre at the Cyxtera Data Centre Campus, a popular data centre campus in Slough - a distance of around 35km. This creates a linear plot from which we can see Sneakernet's carbon emissions break even to the Internet's at a data size of 1348.2GB; that is just one or two regular-sized hard drives! This is even better with electric vehicles; Royal Mail plans to switch to the electric Arrival van, which at full capacity stores 139kWh with a range of 340km \citep{hubbard2021new}. If charged using fossil-fuel generated electricity (the worst-case scenario) this emits 94g CO2e/km, meaning we 'break even' on SneakerNet at 658GB, which one could probably fit on a single laptop. \newline

@@

A great case study where badly thought-through tree planting has been destructive for the Earth was the UK Government's 1981 Forestry Grant Scheme. To increase the UK's timber supply, the UK Government offered huge tax concessions to people who planted trees. \citep{watkins1983public} This concession was incredibly attractive to the super-rich, and soon people started looking for large tracts of land to plant these trees. Eyes moved to the Flow Country in the Scottish Highlands - a vast peatland, the largest bog in Europe. Roughly 500,000 hectares (5000 square kilometres) were drained and planted with conifers before the ecological importance of the Flow Country was recognised and the scheme ended; this was eventually done for the protection of habitats. The other importance of the Flow Country, unknown at the time, was the incredible carbon storage potential of the peatland; peatland bogs only make up 3\% of the world's land area, but store up to a \emph{quarter} of all the world's soil carbon. \citep{turetsky2015global} And when they're drained, they emit carbon rather than storing it; roughly 2 billion \emph{tonnes} of carbon dioxide are emitted from drained peatlands, making 5\% of all global human-created greenhouse gas emissions; not to mention that the trees planted on top of it grew poorly in the soil, and were essentially useless as timber. A badly-planned and badly-informed piece of environmental policy in the 1980s thus left huge ecological damage that Scotland is still working on repairing even today. \citep{gewin2020peat} \newline

One could make the analogy that carbon offsetting is the climate equivalent of the payday loan. Sure, your carbon output will balance out (over infinite time), but if you can help it you'd do better to just leave the fossil fuels in the ground in the first place - and worse, a badly thought-out payday loan could put you in worse financial straits than you were in to start with.
